ECML/PKDD 2016 Discovery Challenge \\ Bank Branch Visits and Customer Acquisition Prediction using Gradient Boosted Trees

### 2016-09-08 paper/paper.tex
update

We only applied stacking for task 2 but not task 1.
We tried two stacking method separately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

@@

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds is a common choice as it provides minimal information loss, we finally decided using 2-folds for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two different time periods. If folds are split by time,
  stacking feature is built based on information from another time period, which is useful to avoid overfitting.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=95mm]{Rplot.png}
\caption{Task 2 $AUC$ of 5-folds CV result (Same parameters) and Prediction on 30\% testing data using different number of stacking features.
 The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}

>>>>

We only applied stacking for task 2 but not task 1.
We tried two stacking methods separately:
\begin{enumerate}
 \item 2-folds stacking split by two time frames

@@

Since stacking index must be fixed in order to avoid leakage, we can only use either 2-folds or 10-folds stacking.
Although 10-folds stacking is a common choice as it provides minimal information loss, we finally applied 2-folds stacking for two reasons:
\begin{enumerate}
 \item The training data is a combination data in two different time periods. If folds are split by time,
  stacking feature is built based on information from another time period, which is useful to avoid overfitting.

@@

\begin{figure}[ht!]
\centering
\includegraphics[width=102mm]{Rplot.png}
\caption{Task 2 $AUC$ of 5-folds CV result (Same parameters) and Prediction on 30\% testing data using different number of stacking features.
 The error bar represents one standard deviation of the CV score. \label{overflow}}
\end{figure}
